%%% Acknowledgments.tex<2> --- 
%% 
%% Filename: Acknowledgments.tex<2>
%% Description: 
%% Author: Ola Leifler
%% Maintainer: 
%% Created: Wed Nov 10 09:45:11 2010 (CET)
%% Version: $Id$
%% Version: 
%% Last-Updated: Tue Jun 21 13:28:03 2016 (+0200)
%%           By: Ola Leifler
%%     Update #: 6
%% URL: 
%% Keywords: 
%% Compatibility: 
%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% 
%%% Commentary: 
%% 
%% 
%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% 
%%% Change log:
%% 
%% 
%% RCS $Log$
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% 
%%% Code:

\swedishenglish{\chapter*{Författarens tack}}{\chapter*{Acknowledgments}}

Foremost, I would like to extend my deepest gratitude to my internal supervisor, Annika Tillander, for her insightful comments, feedback, and continuous support. I cannot stress enough her patience, availability, compassion, and constructive criticism enough.

I am also extremely grateful to my external supervisor, Mike Andersson, who offered me this project in the first place and whose support was indispensable throughout this thesis. Our formal and casual conversations, lab visits, and meetings surely made an already exciting topic even more enjoyable.

Moreover, I am deeply indebted to have José M. Peña as my examiner. I feel he greatly enhanced my work through his thorough review, appreciation, meaningful comments and valuable suggestions.

Special thanks to Lida Khajavizadeh, who was co-responsible for lab experiments and data collection.

I’d like to acknowledge the assistance of my colleagues Erik Rosendal and Mudith Chathuranga Silva, who helped shape this report via proof-reading and excellent suggestions. For that, I thank you.

Additionally, I would like to thank my friends Agustín Valencia, Bayu Brahmantio, José Mendez, and Ismail Khalil for their continuous support and meaningful discussions during our thesis work.

Finally, I would like to dedicate this work to my beloved parents, Katia and Marcio. Unfortunately, there is not enough space in this thesis to even begin describing how grateful I am to them.

To all of you, I offer my sincere appreciation, respect, and gratitude.

\null\hfill Sincerely,

\null\hfill Marcos Freitas Mourão dos Santos


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Acknowledgments.tex<2> ends here

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "demothesis"
%%% End: 
